---
title: "Gráficos en R"
author: "Luis Balderas Ruiz"
date: "11/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# EJERCICIO 1

Plot distance against stretch.

```{r}

library("ggplot2")
stretch = c(46,54,48,50,44,42,52)
distance = c(148,182,173,166,109,141,166)
datos = data.frame(stretch,distance)

p = ggplot(datos, aes(x=datos$stretch, y=datos$distance))
p = p + geom_point()
p
```

# EJERCICIO 2
The table on the right have ten observations, taken during the years 1970-79, are on October snow cover for Eurasia (snow cover is in millions of square kilometers).

- Plot snow.cover versus year
- Plot a histogram of the snow.cover values.

```{r}
year = 1970:1979
snow.cover = c(6.5,12.0,14.9,10.0,10.7,7.9,21.9,12.5,14.5,9.2)
tabla = data.frame(year,snow.cover)
p = ggplot(tabla, aes(x=tabla$year, y=tabla$snow.cover))
p = p + geom_point()
p = p + labs(title="Ejercicio 2", x="Year", y="Snow cover")
p
```
```{r}
q = ggplot(tabla, aes(tabla$snow.cover)) + geom_histogram(binwidth=2)
q
```

# EJERCICIO 3

Given the data in NY.xls

- (Optional) convert ºF to ºC and in to mm.
- Plot Year vs. Warmest Minimum Temperature
- Plot Year vs. Warmest Minimum Temperature and Coldest Minimum Temperature. Don’t forget to add a legend!

Defino una función para transformar las temperaturas de grados Fahrenheint a Centígrados:
```{r}
FahrenheittoCelsius = function(c){
  return((c-32)*(5/9))
}
```

A continuación, transformo las columnas que contienen temperatura:

```{r}
data = read.csv("weather_data_nyc_centralpark_2016.csv")
data$maximum.temerature = FahrenheittoCelsius(data$maximum.temerature)
data$minimum.temperature = FahrenheittoCelsius(data$minimum.temperature)
data$average.temperature = FahrenheittoCelsius(data$average.temperature)
```